Introducing Statistical Design of Experiments to SPARQL Endpoint Evaluation

### 2013-10-16 exp1/present2013.tex
objkective statement
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@686 43ef1190-90fd-4dd7-a769-d0121f02b80e

  \begin{block}{Message for the takeaway}
    If you develop techniques for performance enhancements of complex
    systems, you need to think carefully about how you prove that 
    you've achieved something of general validity. This is my proposal
    in that direction.
  \end{block}

>>>>

  \begin{block}{Message for the takeaway}
    If you make assertions about performance enhancements of complex
    systems, you need to think carefully about how you prove that 
    you've achieved something of general validity. This is my proposal
    in that direction.
  \end{block}
